---
title: "Writing sharable (R) code. Uh... and sharing it!"
author: "Maria Kalimeri, Senior Data Scientist @ [Nightingale Health](https://nightingalehealth.com/)"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "figures/README-",
  message = FALSE, 
  eval = FALSE
)
```


## Intro 

In this tutorial we will build an R package, write unit tests for it
(steps 1-7), push it in a GitHub repository and integrate Travis CI 
with it (step 8). In step 9 we build a drat repository to host this 
and other R packages, using GitHub as a Web Server and set up Travis CI to
automatically push updates of our package into drat. In step 10 we make some 
improvements in the package. We finish with providing sources for R package 
development and other relevant topics.

## Prerequisites

- (Optional) Rstudio; this is not necessary to produce R packages but it 
does make your life easier as the main package for R package development,
`devtools`, is well integrated with RStudio.
- The following R packages: 
    - `devtools` and `roxygen2` in order to build R packages 
    - `tidyverse`, `rlang`
    - `drat`
- (Optional) A github account. If you wish to replicate steps 8 onwards herein 
you need your own github account. You also need a Travis-CI account for which you
can sign up with your github account.

## Create an R package

Let's jump right into it by building 
a minimal R package following [Hilary Parker's building steps](https://hilaryparker.com/2014/04/29/writing-an-r-package-from-scratch/). 
Afterwards, we can discuss when or why to build an R package along with some good 
practices. Most of the discussed topics below are taken from 
Hadley Wickham's [R packages](http://r-pkgs.had.co.nz/).

### Step 1: Create a package directory 

Hilary is building a cat-themed package, but in order to not discourage 
dog persons, I will go with a different theme. Let's make a package whose aim is
to perform some basic statistics on blood metabolomics data. 
(In fact, other than the slightly grotesque namings, the package's single
demo utility has nothing specific to blood metabolomics; we will however add 
simulated metabolomics dataset in our package's examples later on.) 

Let's create the minimum amount of subdirectories your package needs.

```{r}
# Navigate to the desired parent directory
setwd("parent_directory")
# Create the directory of your package with the minimum amount of subdirectories
# Its reasonable but not necessary to name the directory with the same name as 
# the package 
usethis::create_package("bloodstats")
# If you run the above in RStudio, you will likely get a new RStudio window open
# automatically, with the project name "bloodstats"
```

(Alternatively, from within `RStudio`, you may perform the step above by going to 
`File` -> `New Project...` -> `New Directory` -> `R package`, type in the 
package name and location and click `Create Project`. Notice, you may also add 
existing functions at this step.)

What the above function did was to create a directory called `bloodstats/`, 
inside the `parent_directory/`, and inside `bloodstats/` two subdirectories, 

- `R/`, that will soon contain the package source code and
- `man/`, that will soon contain the package's documentation. 

Finally, there are two files, `DESCRIPTION` and `NAMESPACE`. Go ahead and edit 
the `DESCRIPTION` file with a short description of the package, your name and 
contact information, etc. This is the file where you'll also be keeping track 
of your package versioning. 

Here is an example of how I would have my first version of the `DESCRIPTION` 
look like:

```
Package: bloodstats
Title: Utilities for Metabolomics Data
Version: 0.0.0.9999
Authors@R:
    person(
        "Maria", "Kalimeri", email = "maria.kalimeri@nightingalehealth.com",
        role = c("aut", "cre")
    )
Description: Functions and other utilities for basic statistics on blood 
    metabolomics data.
Depends:
    R (>= 3.5.0)
License: MIT + file LICENSE
Encoding: UTF-8
LazyData: true
RoxygenNote: 6.1.1
```

[The package's namespace](http://r-pkgs.had.co.nz/namespace.html), 
as recorded in the `NAMESPACE` file, is something you should understand if you 
plan to share your packages. Namespace takes care of imports and exports such 
that your package will coexist in harmony with other packages. The file 
`NAMESPACE` is something you shouldn't edit by hand, instead `roxygen2` will 
take care of updating this file everytime you build your documentation. 

An important note concerning the name of your package, especially if you plan 
to share it with others. It's good to make sure that the name of your package 
is not already in use by another CRAN package. You can check this by loading 
`https://cran.r-project.org/web/packages/bloodstats`. 

> The License field can be either a standard abbreviation for an open source license, like GPL-2 or BSD, or a pointer to a file containing more information, file LICENSE. The license is really only important if you’re planning on releasing your package. If you don’t, you can ignore this section. I have added an MIT license here just for demonstrational purposes.

### Step 2: Add functions

Below is an example of a function that fits the scope of our package. It takes
a data frame as input (supposedly containining blood biomarkers) and returns 
the mean value of each column (variable) as long as this is numeric.

```{r, eval = FALSE}
bloodmeans <- function(df) {
  df %>%
    dplyr::summarise_if(is.numeric, mean, na.rm = TRUE)
}
```

Save this function as `bloodmeans.R` inside the `R` subdirectory.

> Good to know
> 
> Note the usage of the pipe `%>%` symbol above. The pipe is a way to write a series of operations on an R object, e.g. a data frame, in an easy-to-read way. As an example, the operation `x %>% f(y)` effectivly means `f(x, y)`. You can read more on the pipe [here](https://cran.r-project.org/web/packages/magrittr/vignettes/magrittr.html).
> 
> Furthermore, `summarize_if` is a function of the `dplyr` package, that is part 
> of the core tidyverse, an opinionated collection of R packages designed for data science. If you are not a tidyverse user, I strongly suggest to give it a try. A good place to start is H. Wickham's book ["R for Data Science"](https://r4ds.had.co.nz/)


### Step 3: Add documentation 

What you need to do is type each function's description and other comments at the 
beginning of each function in the form of special comments and `roxygen2` will 
take care of building the whole documentation. An example of how the special 
comments that constitute object documentation should be is shown below. For more information on the subject see [here](http://r-pkgs.had.co.nz/man.html).  

```{r, eval = FALSE}
#' Extract Mean Values of Blood Biomarkers  
#' 
#' This function accepts a dataframe as input and extracts the mean value of 
#' each numeric variable.
#' 
#' @param df a \code{data.frame} with at least one numeric variable in order to 
#' get a non-empty result.
#' @return a data.frame with the mean values of each numeric 
#' @importFrom dplyr summarise_if
#' @author John Doe 
#' @export 
#' @examples 
#' library(magrittr)
#' data.frame(x1 = c(1,2,3), x2 = c(4,5,6)) %>% 
#'   bloodstats::bloodmeans()
bloodmeans <- function(df) {
  df %>%
    dplyr::summarise_if(is.numeric, mean, na.rm = TRUE)
}
```

It is not necessary to have each function in its own file - although it usually 
makes the code easier to read/access by others - but when you add more than one 
function in a file make sure to add the documentation for each function 
just before its definition.

Some notes on documentation. I find it always very usefull to have at least one 
example per function. Even for a "quick and dirty" package, working examples are 
sometimes saving the day. Especially if you need to demonstrate the structure 
of the function's input parameter(s). Such a thing may need one or two built-in datasets. We will add a demo dataset, a couple of steps later. 

Let's take a moment and look at the package's `NAMESPACE` now. In the above code
notice two things, first the explicit call `dplyr::summarise_if` and second, at
the documentation chunck, the entry: 

```
#' @importFrom magrittr %>%
```

They both make sure that you package will have all needed imports for this 
function to work, i.e. packages `dplyr` and `magrittr` in this case. At this point
we need to add these two dependencies in the file `DESCRIPTION` but let's not
do it yet. Simply for demo purposes, we will let `devtools::check()` pick up 
this error a bit later on. 


### Step 4: Process documentation 

You can now use `devtools::document()` to build your documentation. From within 
the package directory, type the following:

```{r, eval = FALSE}
# If you are using an RStudio project for your package development you are most 
# likely already in the package directory. If not, navigate into it
# > setwd("./bloodstats")
# and type:
devtools::document()
```

This function is a wrapper for `roxygen2::roxygenize()`; it adds `.Rd` to the 
`man` directory, one for each object in your package, assuming you have written 
comments as suggested in step 3. The function will also update the `NAMESPACE` 
file of the main directory with the corresponding imports and exports.

> If you see the following warning: 
> ```Warning: The existing 'NAMESPACE' file was not generated by roxygen2,`and will not be overwritten.```
> go ahead and remove the file `NAMESPACE` from the root directory. After you
> do so, re-run the `devtools::document()` command above.

### Step 5: Run checks 

`devtools::check()` or 
[`R CMD check`](http://r-pkgs.had.co.nz/check.html#check) will check your code 
for common issues like documentation mismatches, missing imports etc, including 
pass or fail of unit tests if such exist. 

You should probably run checks quite often. This will help to start curing 
problems and incosistencies as soon as they appear rather than having to deal 
with a huge amount of them at a much later stage. 

So run the command below

```{r, eval = FALSE}
devtools::check()
```

or use the RStudio build-in shortcuts if you prefer. 

Unless you added the `dplyr` and `magrittr` dependencies in your `DESCRIPTION`
above, the check command should now throw an error at the "checking package dependencies"
stage. To fix this open `DESCRIPTION` and update it as shown below:

```
Package: bloodstats
Title: Utilities for Metabolomics Data
Version: 0.0.1
Authors@R:
    person(
        "Maria", "Kalimeri", email = "maria.kalimeri@nightingalehealth.com",
        role = c("aut", "cre")
    )
Description: Functions and other utilities for basic statistics on blood 
    metabolomics data.
Depends:
    R (>= 3.5.0)
Imports:
    dplyr,
    magrittr
License: MIT + file LICENSE
Encoding: UTF-8
LazyData: true
RoxygenNote: 6.1.1
```

After running checks again, there should still be a warning 

```
❯ checking DESCRIPTION meta-information ... WARNING
  Invalid license file pointers: LICENSE
```

which happens as there is a pointer to a file LICENSE that just doesn't exist.
The MIT license is a 'template', so if you use it, you need `License: MIT + file LICENSE`, 
and a LICENSE file that looks like this:

```
YEAR: <Year or years when changes have been made>
COPYRIGHT HOLDER: <Name of the copyright holder>
```

You can add these lines in a file called `LICENSE` in the package root and 
run `devtools::check()` again.

> Notice in the `DESCRIPTION` above that I now increased the version of our 
package from the development version 0.0.0.9999 to 0.0.1
 
### Step 6: Write tests 

This is an important part of package development. The main aims of writing 
formal tests is to make sure, that you will not break code that used to 
work, when you come back in the future to add features or improve existing code. 

You can use `usethis::use_testthat()` to set up the package to use tests. This 
command will do all the necessary steps below: 

1. Create a tests/testthat directory.
2. Adds testthat to the `Suggests` field in the `DESCRIPTION`. The `Suggests` 
lines indicate that while your package can take advantage of a package, this is 
not required to make it work.
3. Create a file tests/testthat.R that runs all your tests when R CMD check 
runs. (See more on automated checking [here](http://r-pkgs.had.co.nz/check.html#check).)

The next step is to actually write the tests. We have only one function at the 
moment, `bloodmeans()`. Create an R file with the name `test-bloodmeans.R`, save 
it in subdir `./tests/testthat/` and type in the following contents.

```{r, eval = FALSE}
context("bloodmeans")

library(magrittr)

res <-
  data.frame(var1 = c(1, 2, 3), var2 = c(4, 5, 6)) %>%
  bloodstats::bloodmeans()

test_that("bloodmeans returns output of expected class", {

  expect_true(
    class(res) == "data.frame"
  )
})

test_that("bloodmeans returns expected result given input", {

  expect_true(
    all(res == data.frame(var1 = 2, var2 = 5))
  )
})

```

You may now run the tests:

```{r, eval=FALSE}
devtools::test()
```

Or you may use the RStudio build-in shortcuts. 

Note that as soon as you add tests in your package, `devtools::check()` will
also include them in the check step. 

Refer to the related section in [R-packages:tests](http://r-pkgs.had.co.nz/tests.html) for more info on proper 
unit testing.

### Step 7: Install your package

From the root directory of the `bloodstats` folder, type the 
following.

```{r, eval = FALSE}
devtools::install(".")
```

That will get your package installed in your machine. You can try viewing the 
documentation of your function by typing 

```{r, eval = FALSE}
?bloodmeans
```


## Share your R package

### Step 8: Make the package a GitHub repo

If you want to reproduce the steps from here onwards you will need a [github](https://github.com/) account.

Just as Hilary in her post, we will not dive into git and GitHub here (let me 
also refer to [Karl Broman’s Git/GitHub Guide](http://kbroman.org/github_tutorial/)
for that). For the purposes of this tutorial, I will assume some basic knowledge
of git. If you don't have it, it's ok, you may simply copy-paste the git commands
here, and come back to it later for details.

#### Step 8a: Push initial commit 
Let us follow the steps 
[in this guide](https://help.github.com/en/articles/adding-an-existing-project-to-github-using-the-command-line) 
in order to create a GitHub repository for our existing R package. Do make the 
following addition though: between steps 4 and 5, add a file with the name 
`.gitignore` with at least the following contents which constitute example lines
of .gitignore contents for an R package repository.

```{r, eval = FALSE}
.RData
.Rhistory
.Rproj.user
.Ruserdata
```

> If a macOS user you may also want to gitignore `.DS_Store`

`.gitignore` contains the names of files that you don't want to include in your 
git repository; so instead of not staging them every time you commit, you 
permanently ignore them by adding them in this file. 

#### Step 8b: Add a README

This is an important step so that people that land in your github repository
page will have an overview of your project. 

Create a file README.md in the root of your package directory with the following
contents.

```
bloodstats
----------

A package with utilities for basic statistics on blood biomarkers.
```

Alternatively, as an R user, especially if you use RStudio, it's handy to use an 
`Rmarkdown`  document to write your description. 
Create a file called `README.Rmd` (remember to add this into a file called 
`.Rbuildignore`  in the top level of the package directory so that `devtools::check()` wont 
give you additional notes about non-standard files in your package folder) 
with the contents suggested below.

> When you copy-paste the README contents below remember to remove the backslash 
"\\" before the chuck ``` definitions 


```
---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# bloodstats

A dummy package for demo and testing. 

## Installation

\```{r, eval = FALSE}
# # Install devtools if you don't have it already
# install.packages("devtools")
devtools::install_github("mariakalimeri/bloodstats")
\```


## Examples

\```{r, eval = FALSE}
data.frame(var1 = c(1, 2, 3), var2 = c(4, 5, 6)) %>%
  bloodstats::bloodmeans()
\ ```

```

If you use the Rmd approach, remember to `knitr::knit()` your document in order to  
have a README.md final output. 

It's good to enrich your `README` with quick, getting-started examples and other 
notes. I often try to browse around other GitHub repositories to explore good 
practices, see for example the `README` file for [`patchwork`](https://github.com/thomasp85/patchwork). 

Add, commit and push your newly created `README.Rmd` and `README.md` files.

```
git status
git add README*
git commit -m "add README"
git push -u origin master
```

#### Step 8c: Enable Travis-CI for your package's repository 

This step requires that you have a Travis-CI account (enabled with your GitHub
account). 

> From your global GitHub > Settings > Applications > Authorized OAuth Apps, make
sure you have granted access to Travis-CI.

Locally, add a file called `.travis.yml` in the root directory of your package. 
Below are the suggested contents. 

```
# R for travis: see documentation at https://docs.travis-ci.com/user/languages/r
  
language: R
cache: packages
```

Add, commit and push your newly added `.travis.yml` file.

```
git status
git add README*
git commit -m "add .travis.yml"
git push -u origin master
```

On the browser, in your Travis-CI account, go to Settings (upper right corner) 
got to Settings and enable Travis-CI for `bloodstats`. If you don't see 
`bloodstats` in the list of repositories, then sync your GitHub account using
the `Sync account` button on the upper left side and refresh the webpage.

You may now find `bloodstats` in your active repositories in your Travis-CI
dashboard, where you can click on `Trigger a build` button.

Fingers crossed and your build will pass!

Finally, open your README.Rmd and add a travis CI status icon if you wish. You
can find and copy the `Status Image` if you click on the `build | unknown` icon 
next to the Travis-CI project title on the travis-ci webpage. Choose an icon for the 
master branch (in the first drop down menu) and Markdown (in the second drop
down menu). The two lines of code that you should add to the README file
will will look like below.

```
[![Build Status](https://travis-ci.org/mariakalimeri/bloodstats.svg?branch=master)](https://travis-ci.org/mariakalimeri/bloodstats)
```

> Step 9 is in the draft phase.

### Step 9: Create your own R package drat repository

#### Step 9a: Create a `drat` git repository in GitHub

[source: Drat for package authors](http://eddelbuettel.github.io/drat/DratForPackageAuthors.html)

As a package author with a given GitHub account, in order to create your own 
R package drat repository, all that is needed is a GitHub repository named 
`drat` and inside it a the subdirectory `src/contrib/`.  

In a terminal, let's create the `drat` folder with its contents and initialize
a git repository for it. Let's place this `drat` directory in the same parent 
directory as `bloodstats`. 

```
mkdir drat 
cd drat
mkdir src
cd src
mkdir contrib
```

Follow the same steps as in *Step 8a* above, in order to create a git repository
for this drat and push its contents in GitHub.

The next step is to place a package into drat. 

Let us built the source package for `bloodstats` to insert it into `drat`. 
Assuming your current working directory is bloodstats type the follwoing


```{r, eval = FALSE}
devtools::build()
```

This will create the file `bloodstats_0.0.1.tar.gz` in the parent directory of
`bloodstats`.

```{r, eval = FALSE}
## insert the bloodstats bundle into the drat repo on local file system
## First change location to the parent directory
setwd("../")
drat::insertPackage("bloodstats_0.0.1.tar.gz", "drat")
```

Git add, commit and push the latest update of this repo to GitHub. 

The next step you need to do is turn on GitHub pages for `drat`. You do this by 
going to the GitHub settings of drat and scroll down to the `GitHub Pages` section.
Choose `master` as your source branch (unless you have a good reason to choose 
otherwise).

Technically, you now have a drat repository of your own, with its first package 
in it! Hurray!! You may very well keep this up-to-date manually as you did just 
now. 

Your friend, the R user that wants to use your collection of packages, as well as
have an easy way to update them, has already been told that your R package repository 
is hosted in a GitHub repository named drat (e.g. https://mariakalimeri.github.io/drat/`).
He now needs to add your drat repo to his list of R repositories:

```{r}
drat::addRepo("mariakalimeri")
```

and he is good to go. E.g. he may type 

```{r}
available.packages(repos = getOption("repos")["mariakalimeri"])
```

and hopefully see the available `bloodstats` packages sitting there happily with
all its info. He can install and update packages the R-usual way, i.e.

```{r}
install.packages("bloodstats")
```

> Mind that `drat::addRepo()` will add the new R repository only in the current
running R session. To update your R repository list more permanently, open your 
`~/.Rprofile` and type 
> ```
> local({
>   r <- getOption("repos")
>   r["CRAN"] <- "https://cran.rstudio.com/"
>   r["mariakalimeri"] <- "https://mariakalimeri.github.io/drat/"
>   options(repos = r)
> })
> ```
> where above I am also selecting the RStudio CRAN mirror.

#### Step 9b: Combining Drat and Travis CI

A next step is to allow Travis-CI to push automatic updates of `bloodstats` into 
drat. To achieve this, use the link below and follow the steps in the `workflow` 
section.

[source: Use Travis CI for automatic pushes of succesfull builds into drat](https://cran.r-project.org/web/packages/drat/vignettes/CombiningDratAndTravis.html)

### Step 10: Improve package and update!

#### Step 10a: Improve existing function

Let us add an extra input parameter, `var`, in `bloodmeans()`. If `var` is 
specified, and it's a valid `df` variable, the function will attempt to group
the input data frame by it and return means for each group.

Update `bloodmeans.R` with the following and try running tests for your package. 
Do they go through?

```{r, eval = FALSE}
#' Extract Mean Values of Blood Biomarkers
#'
#' This function accepts a dataframe as input and extracts the mean value of
#' each numeric variable.
#'
#' @param df a \code{data.frame} with at least one numeric variable in order to
#' get a non-empty result.
#' @param var NULL (default) or the unquoted name of the variable by which to
#' group the input df.
#' @return a data.frame with the mean values of each numeric
#' @importFrom magrittr %>%
#' @author John Doe
#' @export
#' @examples
#' library(magrittr)
#' data.frame(x1 = c(1,2,3), x2 = c(4,5,6)) %>%
#'   bloodstats::bloodmeans()
bloodmeans <- function(df, var = NULL) {

  # Quote input
  var <- rlang::enquo(var)

  if (!rlang::quo_is_null(var)) {
    df <-
      df %>%
      dplyr::group_by(!!var)
  }

  df %>%
    summarise_if(is.numeric, mean, na.rm = TRUE)
}

```

You most likely got an error:

```
test-bloodmeans.R:5: error: (unknown)
could not find function "summarise_if"
```

To fix this substitute `summarise_if` above, with `dplyr::summarise_if`. If your
tests pass now, run `devtools::document()` to update documentation and run also 
a `devtools::check()`. Are the checks clean (is `rlang` dependency in DESCRIPTION?).
When all is ok, bump your package's version number (what should it be?). 
Install the new version locally `devtools::install()`, git add, commit and push 
your updates to GitHub.

```
git status
git add .
git commit -m "add grouping variable in bloodmeans and bump version number"
git push -u origin master
```

The last push to GitHub has hopefully triggered a new Travis-CI built. You can 
check this from your travis-ci account. If your tests passed locally, the travis
built will likely go through as well.

> Step 10b is at the draft phase 

#### Step 10b: Add demo data to the package

Let's create a data frame with random values as carry-on data for this package. 

We will place this in a subdirectory called `data` as is the most common location
for package data. Each file in this directory should be a `.RData` file created by 
`save()` containing a single object (with the same name as the file). The easiest 
way to adhere to these rules is to use `devtools::use_data()`. 

Let's write a small script to first create the data. We will place the script in 
a subdirectory called `data-raw`. We don't need this subdirectory to the 
in the bundled version of the package, so we also add it to `.Rbuildignore`.
We do all the above with the following commant. 

```{r}
usethis::use_data_raw()
```

Create a script `generate_pkg_example_data.R` and save it inside `data-raw`.
The contents of the script are shown below.

```{r, eval = FALSE}
# Create a data frame with random values
#
library(tidyverse)

# Set random seed to make things reproducible
set.seed(34)

# Create data frame
df_example <-
  tibble(id = rep(paste0("id_", seq(1, 50)), 2),
         biofluid = rep(c("blood", "urine"), each = 50),
         males = sample(1:100, size = 100),
         females = sample(1000:1200, size = 100))

usethis::use_data(df_example, overwrite = TRUE)
```

The last line will create a folder data and add the example data frame inside it,
in the proper format. (You may also add package `usethis` in the `Suggests` field 
of your `DESCRIPTION` file.)

Finally, you may also update the examples of `bloodmeans()` to demonstrate the 
new feature with parameter `var`

```{r}
# Grouped bloodmeans
bloodstats::df_example %>%
    bloodstats::bloodmeans(var = group)
```

Next step is to add some documentation for the `df_example`. In the `R` 
subdirectory, create a script called `data.R` with the following contents.

```{r}
#' Random Metabolic Data
#'
#' A dataframe with random data for blood and urine, males and females.
#'
#' @format A data frame (tibble) with 100 rows and 4 columns.
#' \describe{
#'   \item{id}{ID of individual.}
#'   \item{biofluid}{Biofluid type, blood or urine}
#'   \item{males}{Log odds for incident type 2 diabetes.}
#'   \item{females}{Standard error.}
#' }
#' @source Generated with a random \code{set.seed(34)}
"df_example"
```

Rerun `devtools::document()`, `devtools::check(document = FALSE)` and if all clear
you can commit and push your changes to GitHub.

There is one thing we didn't do and should have. That is, after updating the 
`bloodmeans()` function to return grouped means if a valid variable name is 
provided, we didn't add a unit test for this case. I will leave this as a take-home
exercise for you. 

## Further discussion on package development

- When to build a package. Examples of practical use cases:
    - Data reading and cleaning functions, specific to the type of data your are
    handling
    - Data analysis workflow with a demo vignette 
    - A set of vusalization tools
- Package scope. Should a package have an overall scope? Is a package with a bunch of relatively unrelated functions or a not-well-defined scope better than no package at all?

> *'There is a lot to learn on package development, but don’t feel overwhelmed. Start with a minimal subset of useful features (e.g. just an R/ directory!) and build up over time. To paraphrase the Zen monk Shunryu Suzuki: “Each package is perfect the way it is — and it can use a little improvement”.'*


## Usefull links and references 

- **Take a look at our [`ggforestplot`](https://nightingalehealth.github.io/ggforestplot/index.html), Nightingale's first open source R package!!** Website made with [`pkgdown`](https://pkgdown.r-lib.org/articles/pkgdown.html)
- [R packages by Hadley Wickham](http://r-pkgs.had.co.nz/)
- [Karl Broman’s Git/GitHub Guide](http://kbroman.org/github_tutorial/)
- [How to create a GitHub repo from an existing directory](https://help.github.com/articles/adding-an-existing-project-to-github-using-the-command-line/)
- [How to create a GitHub page for your project](https://help.github.com/categories/github-pages-basics/)
- [Tidy evaluation](https://cran.r-project.org/web/packages/dplyr/vignettes/programming.html) and 
[most common actions](https://edwinth.github.io/blog/dplyr-recipes/)
- [R code styler](https://www.tidyverse.org/articles/2017/12/styler-1.0.0/)
- [Software semantic versioning](https://semver.org/)


